### 2016-09-12 notions.tex
no message

First, a set~$S$ is chosen according to some
distribution~$\distr{}{}$ over the collection of multisets
$\mathcal{S}$ associated with~$\Pi$, and then
$\Rep(S)$ is run to generate $(\pubaux,\privaux)$. \jnote{I thought we were going to let
the adversary choose~$S$?} \tsnote{Email discussion. At this point,
I'm happy just making~$S$ part of the experiment ``name'', the
way~$\distr{}{}$ is now.  The distribution seems not to matter for
correctness, at least for the schemes we consider.} \jnote{If instead we choose $S$ from ${\cal D}$, then
is it clear we want to give $S$ to~$A$?} \tsnote{For \emph{correctness},
yes, if for no other reason than to allow~$A$ to know when it asking
a pointless query.  But also it will make no difference to the
provable correctness of the constructions we consider.}
\jnote{OK, I think I would just change the definitions so that the attacker
chooses $S$.}
%(Unless stated otherwise, we assume security holds for all distributions and thus for all sets $S$.)
Adversary~$A$ is given~$\pubaux$~as input; it is also
provided with access to an oracle~$\TestOracle$ that, on input a query~$q \in \calQ$,
returns $\Qry(\pubaux,\privaux,q)$ and increments
a counter if this result is in error.  The adversary wins if it
manages to cause at least~$r>0$ such errors among its queries.
\jnote{If we are specializing the set-multiplicity data structures then we
may as well have the attacker query $x$ which gets translated to query $q_x$. If
we are trying to be more general then we should be consistent.}
\tsnote{I don't see how this correctness notion is specialized to
  set-multiplicity data structures.  I don't think we actually
  specialize notions in any way until, maybe, the OW privacy notion.
  It is true that we only deliver concrete results for set-multiplicty
data structures, however.}

>>>>

First, the adversary $A$ outputs a set $S$ from among those supported by
the data structure. Then,
$\Rep(S)$ is run to generate $(\pubaux,\privaux)$.
%\jnote{I thought we were going to let
%the adversary choose~$S$?} \tsnote{Email discussion. At this point,
%I'm happy just making~$S$ part of the experiment ``name'', the
%way~$\distr{}{}$ is now.  The distribution seems not to matter for
%correctness, at least for the schemes we consider.} \jnote{If instead we choose $S$ from ${\cal D}$, then
%is it clear we want to give $S$ to~$A$?} \tsnote{For \emph{correctness},
%yes, if for no other reason than to allow~$A$ to know when it asking
%a pointless query.  But also it will make no difference to the
%provable correctness of the constructions we consider.}
%\jnote{OK, I think I would just change the definitions so that the attacker
%chooses $S$.}
%(Unless stated otherwise, we assume security holds for all distributions and thus for all sets $S$.)
Adversary~$A$ is given~$\pubaux$~as input; it is also
provided with access to an oracle~$\TestOracle$ that, on input a query~$q \in \calQ$,
returns $\Qry(\pubaux,\privaux,q)$ and increments
a counter if this result is in error.  The adversary wins if it
manages to cause at least~$r>0$ such errors among its queries.
\jnote{If we are specializing the set-multiplicity data structures then we
may as well have the attacker query $x$ which gets translated to query $q_x$. If
we are trying to be more general then we should be consistent.}
\tsnote{I don't see how this correctness notion is specialized to
  set-multiplicity data structures.  I don't think we actually
  specialize notions in any way until, maybe, the OW privacy notion.
  It is true that we only deliver concrete results for set-multiplicty
data structures, however.}
